---
title: "Simulation study: Assessing accuracy"
author: "Stephanie Hicks"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
   html_document:
        toc: true
        toc_float: true
        highlight: tango
        number_sections: true
---

# Summary

In this set of simulations, we simulate a mixture of gaussian 
distributions for cells from three clusters. We are assessing
the accuracy of _k_-means and `mbkmeans()`. 

# Workspace Setup

```{r, wkspace-setup, results='hide', message=FALSE, warning=FALSE}
library(mbkmeans)

# for data viz 
library(dplyr)
library(cowplot)

# parallization
library(parallel)
# can see how many cores are available
detectCores() 

# number of cores for parallelization
cores <- 1
B <- 100

## load helper functions
for (f in paste0("R/",list.files("R", "\\.(r|R)$"))) {
    source(f)
}
```

Here we simulate a mixture of gaussian data 
for cells from three celltypes / clusters. 
Cells are distributed according to a bivariate
normal in a 2-D biological subspace. Each cell
type has a different x/y center and a different SD.

For example, here we simulate bivariate data and plot
the true cluster locations to show what the true
data structure looks likes. 

```{r}
nC <- 1000  # number of cells
nG <- 500 # number of genes

sim_data <- simulate_gauss_mix(n_cells=nC, n_genes=nG)

# check dimension of observed data
dim(sim_data$obs_data)

# Plot the true cluster locations
ref.cols <- c("blue", "brown1", "gold2")
clust1 <- ref.cols[sim_data$true_cluster_id]

# pdf("simulation-studies/figs/accuracy_batch_size_2D_true_structure.pdf", width=6, height=5)
plot(sim_data$true_data, pch=16, cex=1.5, col=clust1, 
     main=paste0("True structure"))
# dev.off()
```

# Benchmark clustering methods 

Here we set up the `bench_accuracy` function to simulate
data using the `simulate_gauss_mix()` function and then
apply _k_-means using the `stats::kmeans()` function and 
mini-batch _k_-means using the `mbkmeans::mini_batch()` 
function. 

```{r}
bench_accuracy <- function(i, n_cells, 
                           n_genes, k_centers, 
                           batch_size=batch_size, 
                           num_init = num_init, 
                           max_iters = max_iters, 
                           init_fraction = init_fraction, 
                           initializer = initializer, ...) {
    # simulate data 
    sim_data <- simulate_gauss_mix(n_cells=n_cells, 
                                   n_genes=n_genes)
    
    # apply clustering methods 
    kmeans_output <- stats::kmeans(sim_data$obs_data, 
                                   centers=k_centers)
    mbkmeans_output <- mbkmeans::mini_batch(
            sim_data$obs_data, clusters = k_centers, 
            batch_size = batch_size, num_init = num_init, 
            max_iters = max_iters, init_fraction = init_fraction,
            initializer = initializer, ...)

    list(sim_data = sim_data, 
         kmeans_output = kmeans_output, 
         mbkmeans_output = mbkmeans_output)    
}
```

We alos set up the `bench_time` function to simulate
data using the `simulate_gauss_mix()` function and then
apply _k_-means using the `stats::kmeans()` function and 
mini-batch _k_-means using the `mbkmeans::mini_batch()` 
function. Then we extract the compute time from the 
algorithms.

```{r}

bench_time <- function(i, n_cells, n_genes, k_centers, 
                       batch_size=batch_size, 
                       num_init = num_init, 
                       max_iters = max_iters, 
                       init_fraction = init_fraction, 
                       initializer = initializer, ...) {
    # simulate data 
    sim_data <- simulate_gauss_mix(n_cells=n_cells, 
                                   n_genes=n_genes)
    
    # apply clustering methods 
    kmeans_time <- system.time(stats::kmeans(sim_data$obs_data, 
                                   centers=k_centers))[3]
    mbkmeans_time <- system.time(mbkmeans::mini_batch(
            sim_data$obs_data, clusters = k_centers, 
            batch_size = batch_size, num_init = num_init, 
            max_iters = max_iters, init_fraction = init_fraction,
            initializer = initializer, ...))[3]

    list(sim_data = sim_data, 
         kmeans_time = kmeans_time, 
         mbkmeans_time = mbkmeans_time)    
}
```

## Simulation looking at differences in batch sizes 

Here we simulate data with different `batch_size`s 
in the `mbkmeans::mini_batch()` function. We simulate 
batch sizes of .1, 0.5, 1, 5, 25, 50 and 100 percent
of the data and compare the accuracy to _k_-means. 

To assess accuracy, we will assess: 

1. Adjusted Rand Index
2. Within Clusters Sum of Squares

We will also consider compute time for increasing sizes
for batches when `num_init=1` and `calc_wcss = FALSE`. 

First, let's set up some parameters for all simulation 
studies in this section: 

```{r}
nC <- 1000
nG <- 500
mbkmeans_initializer = "random"
```


### `batch_size = 1` (or .1 percent of data)

```{r}
# simulate data to assess accuracy
save_bs_0001 <- mclapply(seq_len(B),
                  n_cells = nC, n_genes = nG, 
                  bench_accuracy, k_centers = 3,
                  batch_size = nC*.001, num_init = 10, max_iters = 100, 
                  init_fraction = .1, initializer = mbkmeans_initializer, 
                  mc.cores=cores, calc_wcss = TRUE)

# calculate adjusted Rand Index 
ari_output_bs_0001_ari <- bench_accuracy_calculate_ari(save_bs_0001)

# extract wcss
ari_output_bs_0001_wcss <- bench_accuracy_extract_wcss(save_bs_0001)

# simulate data to asses compute time
# and we set: num_init = 1, calc_wcss = FALSE
save_bs_time_0001 <- mclapply(seq_len(B),
                  n_cells = nC, n_genes = nG, 
                  bench_time, k_centers = 3,
                  batch_size = nC*.001, num_init = 1, max_iters = 100, 
                  init_fraction = .1, initializer = mbkmeans_initializer, 
                  mc.cores=cores, calc_wcss = FALSE)

# extract compute time
time_output_bs_0001 <- bench_time_extract(save_bs_time_0001)
```

```{r}
# boxplots
p_bs_0001_ari <- tidyr::gather(ari_output_bs_0001_ari) %>% 
    ggplot(aes(x=key, y = value)) + 
    geom_boxplot() + geom_jitter() + 
    xlab("clustering method") + 
    ylab("adjusted rand index") + 
    ggtitle("batch_size = 1 (0.1% of data)")
p_bs_0001_ari

p_bs_0001_wcss <- tidyr::gather(ari_output_bs_0001_wcss) %>% 
    ggplot(aes(x=key, y = value)) + 
    geom_boxplot() + geom_jitter() + 
    xlab("clustering method") + 
    ylab("within cluster sum of squares") + 
    ggtitle("batch_size = 1 (0.1% of data)")
p_bs_0001_wcss

p_bs_0001_time <- tidyr::gather(time_output_bs_0001) %>% 
    ggplot(aes(x=key, y = value)) + 
    geom_boxplot() + geom_jitter() + 
    xlab("clustering method") + 
    ylab("compute time") + 
    ggtitle("batch_size = 1 (0.1% of data)")
p_bs_0001_time
```

### `batch_size = 5` (or .5 percent of data)

```{r}
# simulate data
save_bs_0005 <- mclapply(seq_len(B), 
                  n_cells = nC, n_genes = nG, 
                  bench_accuracy, k_centers = 3,
                  batch_size = nC*.005, num_init = 10, max_iters = 100, 
                  init_fraction = .1, initializer = mbkmeans_initializer, 
                  mc.cores=cores, calc_wcss = TRUE)

# calculate adjusted Rand Index 
ari_output_bs_0005_ari <- bench_accuracy_calculate_ari(save_bs_0005)

# extract wcss
ari_output_bs_0005_wcss <- bench_accuracy_extract_wcss(save_bs_0005)

# simulate data to asses compute time 
# and we set: num_init = 1, calc_wcss = FALSE
save_bs_time_0005 <- mclapply(seq_len(B),
                  n_cells = nC, n_genes = nG, 
                  bench_time, k_centers = 3,
                  batch_size = nC*.005, num_init = 1, max_iters = 100, 
                  init_fraction = .1, initializer = mbkmeans_initializer, 
                  mc.cores=cores, calc_wcss = FALSE)

# extract compute time
time_output_bs_0005 <- bench_time_extract(save_bs_time_0005)
```

```{r}
# boxplots
p_bs_0005_ari <- tidyr::gather(ari_output_bs_0005_ari) %>% 
    ggplot(aes(x=key, y = value)) + 
    geom_boxplot() + geom_jitter() + 
    xlab("clustering method") + 
    ylab("adjusted rand index") + 
    ggtitle("batch_size = 5 (0.5% of data)")
p_bs_0005_ari

p_bs_0005_wcss <- tidyr::gather(ari_output_bs_0005_wcss) %>% 
    ggplot(aes(x=key, y = value)) + 
    geom_boxplot() + geom_jitter() + 
    xlab("clustering method") + 
    ylab("within cluster sum of squares") + 
    ggtitle("batch_size = 5 (0.5% of data)")
p_bs_0005_wcss

p_bs_0005_time <- tidyr::gather(time_output_bs_0005) %>% 
    ggplot(aes(x=key, y = value)) + 
    geom_boxplot() + geom_jitter() + 
    xlab("clustering method") + 
    ylab("compute time") + 
    ggtitle("batch_size = 5 (0.5% of data)")
p_bs_0005_time
```

### `batch_size = 10` (or 1 percent of data)

```{r}
# simulate data
save_bs_001 <- mclapply(seq_len(B), n_cells=nC, n_genes =nG, 
                  bench_accuracy, k_centers = 3,
                  batch_size = nC*.01, num_init = 10, max_iters = 100, 
                  init_fraction = .1, initializer = mbkmeans_initializer, 
                  mc.cores=cores, calc_wcss = TRUE)

# calculate adjusted Rand Index 
ari_output_bs_001_ari <- bench_accuracy_calculate_ari(save_bs_001)

# extract wcss
ari_output_bs_001_wcss <- bench_accuracy_extract_wcss(save_bs_001)

# simulate data to asses compute time
# and we set: num_init = 1, calc_wcss = FALSE
save_bs_time_001 <- mclapply(seq_len(B),
                  n_cells = nC, n_genes = nG, 
                  bench_time, k_centers = 3,
                  batch_size = nC*.01, num_init = 1, max_iters = 100, 
                  init_fraction = .1, initializer = mbkmeans_initializer, 
                  mc.cores=cores, calc_wcss = FALSE)

# extract compute time
time_output_bs_001 <- bench_time_extract(save_bs_time_001)
```

```{r}
# boxplots
p_bs_001_ari <- tidyr::gather(ari_output_bs_001_ari) %>% 
    ggplot(aes(x=key, y = value)) + 
    geom_boxplot() + geom_jitter() + 
    xlab("clustering method") + 
    ylab("adjusted rand index") + 
    ggtitle("batch_size = 10 (1% of data)")
p_bs_001_ari

p_bs_001_wcss <- tidyr::gather(ari_output_bs_001_wcss) %>% 
    ggplot(aes(x=key, y = value)) + 
    geom_boxplot() + geom_jitter() + 
    xlab("clustering method") + 
    ylab("within cluster sum of squares") + 
    ggtitle("batch_size = 10 (1% of data)")
p_bs_001_wcss

p_bs_001_time <- tidyr::gather(time_output_bs_001) %>% 
    ggplot(aes(x=key, y = value)) + 
    geom_boxplot() + geom_jitter() + 
    xlab("clustering method") + 
    ylab("compute time") + 
    ggtitle("batch_size = 10 (1% of data)")
p_bs_001_time
```


### `batch_size = 50` (or 5 percent of data)
```{r}
# simulate data
save_bs_005 <- mclapply(seq_len(B), n_cells=nC, n_genes =nG, 
                  bench_accuracy, k_centers = 3,
                  batch_size = nC*.05, num_init = 10, max_iters = 100, 
                  init_fraction = .1, initializer = mbkmeans_initializer, 
                  mc.cores=cores, calc_wcss = TRUE)

# calculate adjusted Rand Index 
ari_output_bs_005_ari <- bench_accuracy_calculate_ari(save_bs_005)

# extract wcss
ari_output_bs_005_wcss <- bench_accuracy_extract_wcss(save_bs_005)

# simulate data to asses compute time
# and we set: num_init = 1, calc_wcss = FALSE
save_bs_time_005 <- mclapply(seq_len(B),
                  n_cells = nC, n_genes = nG, 
                  bench_time, k_centers = 3,
                  batch_size = nC*.05, num_init = 1, max_iters = 100, 
                  init_fraction = .1, initializer = mbkmeans_initializer, 
                  mc.cores=cores, calc_wcss = FALSE)

# extract compute time
time_output_bs_005 <- bench_time_extract(save_bs_time_005)
```

```{r}
# boxplots
p_bs_005_ari <- tidyr::gather(ari_output_bs_005_ari) %>% 
    ggplot(aes(x=key, y = value)) + 
    geom_boxplot() + geom_jitter() + 
    xlab("clustering method") + 
    ylab("adjusted rand index") + 
    ggtitle("batch_size = 50 (5% of data)")
p_bs_005_ari

p_bs_005_wcss <- tidyr::gather(ari_output_bs_005_wcss) %>% 
    ggplot(aes(x=key, y = value)) + 
    geom_boxplot() + geom_jitter() + 
    xlab("clustering method") + 
    ylab("within cluster sum of squares") + 
    ggtitle("batch_size = 50 (5% of data)")
p_bs_005_wcss

p_bs_005_time <- tidyr::gather(time_output_bs_005) %>% 
    ggplot(aes(x=key, y = value)) + 
    geom_boxplot() + geom_jitter() + 
    xlab("clustering method") + 
    ylab("compute time") + 
    ggtitle("batch_size = 50 (5% of data)")
p_bs_005_time
```

### `batch_size = 250` (or 25 percent of data)
```{r}
# simulate data
save_bs_025 <- mclapply(seq_len(B), n_cells=nC, n_genes =nG, 
                  bench_accuracy, k_centers = 3,
                  batch_size = nC*.25, num_init = 10, max_iters = 100, 
                  init_fraction = .1, initializer = mbkmeans_initializer, 
                  mc.cores=cores, calc_wcss = TRUE)

# calculate adjusted Rand Index 
ari_output_bs_025_ari <- bench_accuracy_calculate_ari(save_bs_025)

# extract wcss
ari_output_bs_025_wcss <- bench_accuracy_extract_wcss(save_bs_025)

# simulate data to asses compute time
# and we set: num_init = 1, calc_wcss = FALSE
save_bs_time_025 <- mclapply(seq_len(B),
                  n_cells = nC, n_genes = nG, 
                  bench_time, k_centers = 3,
                  batch_size = nC*.25, num_init = 1, max_iters = 100, 
                  init_fraction = .1, initializer = mbkmeans_initializer, 
                  mc.cores=cores, calc_wcss = FALSE)

# extract compute time
time_output_bs_025 <- bench_time_extract(save_bs_time_025)
```

```{r}
# boxplots
p_bs_025_ari <- tidyr::gather(ari_output_bs_025_ari) %>% 
    ggplot(aes(x=key, y = value)) + 
    geom_boxplot() + geom_jitter() + 
    xlab("clustering method") + 
    ylab("adjusted rand index") + 
    ggtitle("batch_size = 250 (25% of data)")
p_bs_025_ari

p_bs_025_wcss <- tidyr::gather(ari_output_bs_025_wcss) %>% 
    ggplot(aes(x=key, y = value)) + 
    geom_boxplot() + geom_jitter() + 
    xlab("clustering method") + 
    ylab("within cluster sum of squares") + 
    ggtitle("batch_size = 250 (25% of data)")
p_bs_025_wcss

p_bs_025_time <- tidyr::gather(time_output_bs_025) %>% 
    ggplot(aes(x=key, y = value)) + 
    geom_boxplot() + geom_jitter() + 
    xlab("clustering method") + 
    ylab("compute time") + 
    ggtitle("batch_size = 250 (25% of data)")
p_bs_025_time
```

### `batch_size = 500` (or 50 percent of data)
```{r}
# simulate data
save_bs_050 <- mclapply(seq_len(B), n_cells=nC, n_genes =nG, 
                  bench_accuracy, k_centers = 3,
                  batch_size = nC*.50, num_init = 10, max_iters = 100, 
                  init_fraction = .1, initializer = mbkmeans_initializer, 
                  mc.cores=cores, calc_wcss = TRUE)

# calculate adjusted Rand Index 
ari_output_bs_050_ari <- bench_accuracy_calculate_ari(save_bs_050)

# extract wcss
ari_output_bs_050_wcss <- bench_accuracy_extract_wcss(save_bs_050)

# simulate data to asses compute time
# and we set: num_init = 1, calc_wcss = FALSE
save_bs_time_050 <- mclapply(seq_len(B),
                  n_cells = nC, n_genes = nG, 
                  bench_time, k_centers = 3,
                  batch_size = nC*.50, num_init = 1, max_iters = 100, 
                  init_fraction = .1, initializer = mbkmeans_initializer, 
                  mc.cores=cores, calc_wcss = FALSE)

# extract compute time
time_output_bs_050 <- bench_time_extract(save_bs_time_050)
```

```{r}
# boxplots
p_bs_050_ari <- tidyr::gather(ari_output_bs_050_ari) %>% 
    ggplot(aes(x=key, y = value)) + 
    geom_boxplot() + geom_jitter() + 
    xlab("clustering method") + 
    ylab("adjusted rand index") + 
    ggtitle("batch_size = 500 (50% of data)")
p_bs_050_ari

p_bs_050_wcss <- tidyr::gather(ari_output_bs_050_wcss) %>% 
    ggplot(aes(x=key, y = value)) + 
    geom_boxplot() + geom_jitter() + 
    xlab("clustering method") + 
    ylab("within cluster sum of squares") + 
    ggtitle("batch_size = 500 (50% of data)")
p_bs_050_wcss

p_bs_050_time <- tidyr::gather(time_output_bs_050) %>% 
    ggplot(aes(x=key, y = value)) + 
    geom_boxplot() + geom_jitter() + 
    xlab("clustering method") + 
    ylab("compute time") + 
    ggtitle("batch_size = 500 (50% of data)")
p_bs_050_time
```

### `batch_size = 1000` (or 100 percent of data)
```{r}
# simulate data
save_bs_100 <- mclapply(seq_len(B), n_cells=nC, n_genes =nG, 
                  bench_accuracy, k_centers = 3,
                  batch_size = nC*1, num_init = 10, max_iters = 100, 
                  init_fraction = .1, initializer = mbkmeans_initializer, 
                  mc.cores=cores, calc_wcss = TRUE)

# calculate adjusted Rand Index 
ari_output_bs_100_ari <- bench_accuracy_calculate_ari(save_bs_100)

# extract wcss
ari_output_bs_100_wcss <- bench_accuracy_extract_wcss(save_bs_100)

# simulate data to asses compute time
# and we set: num_init = 1, calc_wcss = FALSE
save_bs_time_100 <- mclapply(seq_len(B),
                  n_cells = nC, n_genes = nG, 
                  bench_time, k_centers = 3,
                  batch_size = nC*1, num_init = 1, max_iters = 100, 
                  init_fraction = .1, initializer = mbkmeans_initializer, 
                  mc.cores=cores, calc_wcss = FALSE)

# extract compute time
time_output_bs_100 <- bench_time_extract(save_bs_time_100)
```

```{r}
# boxplots
p_bs_100_ari <- tidyr::gather(ari_output_bs_100_ari) %>% 
    ggplot(aes(x=key, y = value)) + 
    geom_boxplot() + geom_jitter() + 
    xlab("clustering method") + 
    ylab("adjusted rand index") + 
    ggtitle("batch_size = 1000 (100% of data)")
p_bs_100_ari

p_bs_100_wcss <- tidyr::gather(ari_output_bs_100_wcss) %>% 
    ggplot(aes(x=key, y = value)) + 
    geom_boxplot() + geom_jitter() + 
    xlab("clustering method") + 
    ylab("within cluster sum of squares") + 
    ggtitle("batch_size = 1000 (100% of data)")
p_bs_100_wcss

p_bs_100_time <- tidyr::gather(time_output_bs_100) %>% 
    ggplot(aes(x=key, y = value)) + 
    geom_boxplot() + geom_jitter() + 
    xlab("clustering method") + 
    ylab("compute time") + 
    ggtitle("batch_size = 1000 (100% of data)")
p_bs_100_time
```


### Summary

First we will combine the boxplots together in 
one plot. 
```{r}
p_out_ari <- plot_grid(p_bs_0001_ari, p_bs_0005_ari, p_bs_001_ari, 
                   p_bs_005_ari, p_bs_025_ari, p_bs_050_ari, 
                   p_bs_100_ari, ncol = 4, 
                   labels = LETTERS[1:7], label_size = 30)
pdf(paste0("simulation-studies/figs/accuracy_batch_size_", 
           mbkmeans_initializer,"_ari.pdf"), width=20, height=10)
print(p_out_ari)
dev.off()

p_out_wcss <- plot_grid(p_bs_0001_wcss, p_bs_0005_wcss, p_bs_001_wcss, 
                   p_bs_005_wcss, p_bs_025_wcss, p_bs_050_wcss, 
                   p_bs_100_wcss, ncol = 4, 
                   labels = LETTERS[1:7], label_size = 30)
pdf(paste0("simulation-studies/figs/accuracy_batch_size_", 
           mbkmeans_initializer,"_wcss.pdf"), width=20, height=10)
print(p_out_wcss)
dev.off()

p_out_time <- plot_grid(p_bs_0001_time, p_bs_0005_time, p_bs_001_time, 
                   p_bs_005_time, p_bs_025_time, 
                   p_bs_050_time, # p_bs_100_time, 
                   ncol = 3, 
                   labels = LETTERS[1:7], label_size = 30)
pdf(paste0("simulation-studies/figs/time_batch_size_", 
           mbkmeans_initializer,".pdf"), width=20, height=10)
print(p_out_time)
dev.off()

```

Then we summarize by taking the average across the `B` 
Monte Carlo simulations and plot the mean and standard 
error for increasing sizes of `batch_sizes`. 

```{r}
dat_ari <- data.frame( 
    rbind(stack(ari_output_bs_0001_ari),  
      stack(ari_output_bs_0005_ari), 
      stack(ari_output_bs_001_ari), 
      stack(ari_output_bs_005_ari), 
      stack(ari_output_bs_025_ari)#, 
      # stack(ari_output_bs_050_ari), 
      # stack(ari_output_bs_100_ari)
      ), 
    "batch_size" = rep(scales::percent(c(.001, .005, .01, .05, .25#, .50, 1.00
                         )), each = B*2))

dat_ari$batch_size <- factor(dat_ari$batch_size, 
       levels=c("0.1%", "0.5%", "1.0%", "5.0%", "25.0%"#, "50.0%, "100.0%"
                ))

p_out_ari <- dat_ari %>% 
    group_by(batch_size, ind) %>% 
    summarize(median_ari = median(values), 
              se_ari = sd(values) / sqrt(n())) %>%
ggplot(aes(x=batch_size, y=median_ari, colour=ind, group=ind)) + 
    geom_line() + geom_point() + 
    geom_errorbar(aes(ymin=median_ari-se_ari, 
                      ymax=median_ari+se_ari), width=.1) +
    xlab("batch size") + 
    ylab("adjusted Rand Index") + 
    theme(legend.position="top")

pdf(paste0("simulation-studies/figs/accuracy_batch_size_", 
           mbkmeans_initializer,"_ari_combined.pdf"), width=10, height=5)
print(p_out_ari)
dev.off()
```

```{r}
dat_wcss <- data.frame( 
    rbind(stack(ari_output_bs_0001_wcss),  
      stack(ari_output_bs_0005_wcss), 
      stack(ari_output_bs_001_wcss), 
      stack(ari_output_bs_005_wcss), 
      stack(ari_output_bs_025_wcss)#, 
      # stack(ari_output_bs_050_wcss), 
      # stack(ari_output_bs_100_wcss)
      ), 
    "batch_size" = rep(scales::percent(c(.001, .005, .01, .05, .25#, .50, 1.00
                         )), each = B*2))

dat_wcss$batch_size <- factor(dat_wcss$batch_size, 
       levels=c("0.1%", "0.5%", "1.0%", "5.0%", "25.0%"#, "50.0%, "100.0%"
                ))

p_out_wcss <- dat_wcss %>% 
    group_by(batch_size, ind) %>% 
    summarize(median_wcss = median(values), 
              se_wcss = sd(values) / sqrt(n())) %>%
ggplot(aes(x=batch_size, y=median_wcss, colour=ind, group=ind)) + 
    geom_line() + geom_point() + 
    geom_errorbar(aes(ymin=median_wcss-se_wcss, 
                      ymax=median_wcss+se_wcss), width=.1) +
    xlab("batch size") + 
    ylab("within cluster sum of squares") + 
    theme(legend.position="top")

pdf(paste0("simulation-studies/figs/accuracy_batch_size_", 
           mbkmeans_initializer,"_wcss_combined.pdf"), width=10, height=5)
print(p_out_wcss)
dev.off()
```


```{r}
dat_time <- data.frame( 
    rbind(stack(time_output_bs_0001),  
      stack(time_output_bs_0005), 
      stack(time_output_bs_001), 
      stack(time_output_bs_005), 
      stack(time_output_bs_025)#, 
      # stack(time_output_bs_050), 
      # stack(time_output_bs_100)
      ), 
    "batch_size" = rep(scales::percent(c(.001, .005, .01, .05, .25#, .50, 1.00
                         )), each = B*2))

dat_time$batch_size <- factor(dat_time$batch_size, 
       levels=c("0.1%", "0.5%", "1.0%", "5.0%", "25.0%"#, "50.0%", "100.0%"
                ))

p_out_time <- dat_time %>% 
    group_by(batch_size, ind) %>% 
    summarize(median_time = median(values), 
              se_time = sd(values) / sqrt(n())) %>%
ggplot(aes(x=batch_size, y=median_time, colour=ind, group=ind)) + 
    geom_line() + geom_point() + 
    geom_errorbar(aes(ymin=median_time-se_time, 
                      ymax=median_time+se_time), width=.1) +
    xlab("batch size") + 
    ylab("compute time (seconds)") + 
    theme(legend.position="top")

pdf(paste0("simulation-studies/figs/time_batch_size_", 
           mbkmeans_initializer,"_combined.pdf"), width=10, height=5)
print(p_out_time)
dev.off()
    

```

