---
title: "Memory_Benchmark"
author: "Ruoxi Liu"
date: "5/17/2019"
output: html_document
---
```{r setup, include=FALSE, warning=FALSE}
library(mbkmeans)
library(rhdf5)
library(HDF5Array)
library(here)
library(profvis)
```

Simulate random data from `rnorm()` and save 
data as a `HDF5Matrix` object. 

```{r}
n_cells <- 5000
n_genes <- 1000

obs_data <- matrix(rnorm(n_cells*n_genes), nrow = n_genes, ncol = n_cells)

saveRDS(obs_data, file = here("ongoing_analysis", "Single Case", "sim_data.rds"))

h5File <- here("ongoing_analysis", "Single Case","sim_data.h5")
h5createFile(h5File)
h5createDataset(file = h5File, dataset = "obs", 
                dims = dim(obs_data), chunk = c(1,n_genes),
                level = 0)
h5write(obs_data, file = h5File, name = "obs" )

rm(obs_data)
invisible(gc())
```

## Memory profiling using `Rprof()`
Apply memory profiling to `stats::kmeans` with data in memory

```{r}
Rprof(filename = here("ongoing_analysis", "Single Case", "Rprof_kmeans.out"), append = FALSE, memory.profiling = TRUE)
obs_data <- readRDS(file = here("ongoing_analysis", "Single Case", "sim_data.rds"))
km_test <- stats::kmeans(obs_data, centers=3, iter.max = 100, nstart = 10)
Rprof(NULL)

profile <- summaryRprof(filename = here("ongoing_analysis", "Single Case", "Rprof_kmeans.out"), 
                        chunksize = 1000000, memory = "both", diff = FALSE)

write.csv(profile$by.total, here("ongoing_analysis", "Single Case", "Rprof_km.csv"))
rm(obs_data)
rm(km_test)
rm(profile)
invisible(gc())
```

Apply memory profiling to `mbkmeans::mini_batch()` with data in memory
```{r}
Rprof(filename = here("ongoing_analysis", "Single Case", "Rprof_mbkmeans.out"), append = FALSE, memory.profiling = TRUE)
obs_data <- readRDS(file = here("ongoing_analysis", "Single Case", "sim_data.rds"))
mbkmeans_test <- mbkmeans::mini_batch(
            obs_data, clusters = 3, 
            batch_size = 50, num_init = 10, 
            max_iters = 100, init_fraction = 0.1,
            initializer = "random")
Rprof(NULL)

profile <- summaryRprof(filename = here("ongoing_analysis", "Single Case", "Rprof_mbkmeans.out"), 
                        chunksize = 1000000, memory = "both", diff = FALSE)

write.csv(profile$by.total, here("ongoing_analysis", "Single Case", "Rprof_mbkm.csv"))
rm(obs_data)
rm(mbkmeans_test)
rm(profile)
invisible(gc())
```

Apply memory profiling to `mbkmeans::mini_batch()` with HDF5 file

```{r}
Rprof(filename = here("ongoing_analysis", "Single Case", "Rprof_hdf5.out"), append = TRUE, memory.profiling = TRUE)
sim_data_hdf5 <- HDF5Array(file = here("ongoing_analysis", "Single Case","sim_data.h5"), name = "obs")
hdf5_test <- mbkmeans::mini_batch(
            sim_data_hdf5, clusters = 3, 
            batch_size = 50, num_init = 10, 
            max_iters = 100, init_fraction = 0.1,
            initializer = "random")
Rprof(NULL)

profile <- summaryRprof(filename = here("ongoing_analysis", "Single Case", "Rprof_hdf5.out"), 
                        chunksize = 1000000, memory = "both", diff = FALSE)

write.csv(profile$by.total, here("ongoing_analysis", "Single Case", "Rprof_hdf5.csv"))
rm(obs_data)
rm(hdf5_test)
rm(profile)
invisible(gc())
```

## Memory profiling using `profvis()`

Apply memory profiling to `stats::kmeans` with data in memory

```{r}
memory_compare1 <- profvis({
  obs_data <- readRDS(file = here("ongoing_analysis", "Single Case", "sim_data.rds"))
  km_test <- stats::kmeans(obs_data, centers=3, 
                           iter.max = 100, nstart = 10)
})

htmlwidgets::saveWidget(memory_compare1, here("ongoing_analysis", "Single Case", "profvis_kmeans.html"))
rm(obs_data)
rm(km_test)
rm(memory_compare1)
invisible(gc())
```

Apply memory profiling to `mbkmeans::mini_batch()` with data in memory

```{r}
memory_compare2 <- profvis({
  obs_data <- readRDS(file = here("ongoing_analysis", "Single Case", "sim_data.rds"))
  mbkmeans_test <- mbkmeans::mini_batch(
            obs_data, clusters = 3, 
            batch_size = 50, num_init = 10, 
            max_iters = 100, init_fraction = 0.1,
            initializer = "random")
})

htmlwidgets::saveWidget(memory_compare2, here("ongoing_analysis", "Single Case", "profvis_mbkmeans.html"))
rm(obs_data)
rm(mbkmeans_test)
rm(memory_compare2)
invisible(gc())
```

Apply memory profiling to `mbkmeans::mini_batch()` with HDF5 file

```{r}
memory_compare3 <- profvis({
sim_data_hdf5 <- HDF5Array(file = here("ongoing_analysis", "Single Case","sim_data.h5"), name = "obs")
hdf5_test <- mbkmeans::mini_batch(
            sim_data_hdf5, clusters = 3, 
            batch_size = 50, num_init = 10, 
            max_iters = 100, init_fraction = 0.1,
            initializer = "random")
})

htmlwidgets::saveWidget(memory_compare3, here("ongoing_analysis", "Single Case", "profvis_hdf5.html"))
rm(sim_data_hdf5)
rm(hdf5_test)
rm(memory_compare3)
invisible(gc())
```

```{r}
library(benchmarkme)
sink(file = here("ongoing_analysis", "Single Case","info.txt"))
print(get_ram())
print(get_cpu())
print(sessionInfo())
sink()
```

