---
title: Preprocessing HCA Cord Blood data
author: Davide Risso, Stephanie Hicks, Ruoxi Liu
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, 
                      error = FALSE, message = FALSE, 
                      cache = FALSE)
```


# Data 

We use one of the Human Cell Atlas preview datasets. 
The preview data are available in the 
[`HCAData` Bioconductor package](https://bioconductor.org/packages/release/data/experiment/html/HCAData.html). In this analysis, we will use the 
`ica_bone_marrow` dataset. 

## Data import 
```{r}
library(HCAData)
library(ExperimentHub)
library(SingleCellExperiment)

eh <- ExperimentHub()
query(eh, "HCAData")

##change to ica_bone_marrow
sce <- HCAData("ica_cord_blood")
sce 

## Check that the counts object is a HDF5Array
seed(counts(sce))
assay(sce)
```

# Quality control and 

## Removing low-quality cells

First, we use the `scater` package to compute a set of 
QC measures and filter out the low-quality samples.

```{r}
library(scater)
system.time(sce <- calculateQCMetrics(sce, 
                          feature_controls = list(Mito = grep("^MT", rowData(sce)$Symbol)),
                          BPPARAM = BiocParallel::MulticoreParam(10)))
```

We remove cells with high proportion of mitocondrial 
reads, using it as a proxy for cell damage. 

```{r}
high_mito <- isOutlier(sce$pct_counts_Mito, 
                       nmads = 3, type="higher")
table(high_mito)

sce <- sce[,!high_mito]
sce
```

## Removing lowly expressed genes

Next, we remove the lowly expressed genes. Here, 
we keep only those genes that have at least 1 UMI 
in at least 5% of the data. These threshold are
dataset-specific and may need to be taylored to 
specific applications.

```{r}
num_reads <- 1
num_cells <- 0.05*ncol(sce)
system.time(keep <- which(DelayedArray::rowSums(counts(sce) >= num_reads ) >= num_cells))
sce <- sce[keep,]
sce
```

These leaves us with `length(keep)` genes.


Save sce object to /data/full
```{r}
library(HDF5Array)
library(here)
saveHDF5SummarizedExperiment(sce, 
                             dir = here("main/case_studies/data/full","hca_cordblood_preprocessed"),
                             prefix="", replace=FALSE, 
                             chunkdim=c(dim(counts(sce))[1],1), 
                             level=NULL, verbose=FALSE)
```

