---
title: Preprocessing TENx Brain Data
author: Davide Risso, Stephanie Hicks, Ruoxi Liu
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, 
                      error = FALSE, message = FALSE, 
                      cache = FALSE)
```

```{r}
#Create the necessary folder structure
library(here)
if(!file.exists(here("main/case_studies/data"))){
      dir.create(here("main/case_studies/data"))
      dir.create(here("main/case_studies/data/full"))
      dir.create(here("main/case_studies/data/pca"))
}

library(doParallel)
ncores <- 5
doParallel::registerDoParallel(ncores)
```

## Data import 
```{r}
library(TENxBrainData)
tenx <- TENxBrainData()
tenx

## Check that the counts object is a HDF5Array
seed(counts(tenx))
assay(tenx)
```

Run the next chunk to pick a subset of cells to debug code.

```{r}
#set.seed(1234)
#keep_cells <- sample(1:ncol(tenx),size = 100)
#tenx <- tenx[,keep_cells]
```

# Quality control and 

## Removing low-quality cells

First, we use the `scater` package to compute a set of 
QC measures and filter out the low-quality samples.

```{r}
library(scater)
system.time(tenx <- addPerCellQC(tenx, 
                          subsets = list(Mito = grep("^mt", rowData(tenx)$Symbol)),
                          BPPARAM = BiocParallel::MulticoreParam(ncores)))
```

We remove cells with high proportion of mitocondrial 
reads, using it as a proxy for cell damage. 

```{r}
high_mito <- isOutlier(tenx$subsets_Mito_percent, 
                       nmads = 3, type="higher")
table(high_mito)

tenx <- tenx[,!high_mito]
tenx
```

## Removing lowly expressed genes

Next, we remove the lowly expressed genes. Here, 
we keep only those genes that have at least 1 UMI 
in at least 5% of the data. These threshold are
dataset-specific and may need to be taylored to 
specific applications.

```{r}
num_reads <- 1
num_cells <- 0.01*ncol(tenx)
system.time(keep <- which(DelayedArray::rowSums(counts(tenx) >= num_reads ) >= num_cells))
tenx <- tenx[keep,]
tenx
```

These leaves us with `length(keep)` genes.


Save tenx object to /data/full
```{r}
library(HDF5Array)
if(!file.exists(here("main/case_studies/data/full/TENxBrainData"))) {
  dir.create(here("main/case_studies/data/full/TENxBrainData"), recursive = TRUE)
}
saveHDF5SummarizedExperiment(tenx,
                             dir = here("main/case_studies/data/full/TENxBrainData", "TENxBrainData_preprocessed"),
                             prefix="", replace=TRUE,
                             chunkdim=c(nrow(tenx),1),
                             level=NULL, verbose=FALSE)

saveHDF5SummarizedExperiment(tenx, 
                             dir = here("main/case_studies/data/full/TENxBrainData", "TENxBrainData_preprocessed_default"), 
                             prefix="", replace=TRUE, 
                             level=NULL, verbose=FALSE)
```

