---
title: Preprocessing TENxPBMC68k Data
author: Davide Risso, Stephanie Hicks, Ruoxi Liu
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, 
                      error = FALSE, message = FALSE, 
                      cache = FALSE)
```

```{r}
#Create the necessary folder structure
library(here)
if(!file.exists(here("main/case_studies/data"))){
      dir.create(here("main/case_studies/data"))
      dir.create(here("main/case_studies/data/full"))
      dir.create(here("main/case_studies/data/pca"))
    }
```

# Data 

We use one of the TENxPBMC Data. 
The preview data are available in the 
[`TENxPBMCData` Bioconductor package](https://bioconductor.org/packages/release/data/experiment/html/TENxPBMCData.html). In this analysis, we will use the 
`pbmc68k` dataset. 

## Data import 
```{r}
library(TENxPBMCData)
tenx_pbmc68k <- TENxPBMCData(dataset = "pbmc68k")
tenx_pbmc68k

## Check that the counts object is a HDF5Array
seed(counts(tenx_pbmc68k))
assay(tenx_pbmc68k)
```

# Quality control and 

## Removing low-quality cells

First, we use the `scater` package to compute a set of 
QC measures and filter out the low-quality samples.

```{r}
library(scater)
system.time(tenx_pbmc68k <- calculateQCMetrics(tenx_pbmc68k, 
                          feature_controls = 
                            list(Mito = grep("^MT", rowData(tenx_pbmc68k)$Symbol)),
                          BPPARAM = BiocParallel::MulticoreParam(10)))
```

Plot Percentage of Mito vs. Total Number of Genes Detected, and Historgrams of UMI & Total Number of Genes Detected
```{r, fig.width=8, fig.height=4}
#par(mfrow=c(1,3))
#plot(tenx_pbmc68k$total_features_by_counts,tenx_pbmc68k$pct_counts_Mito, ylab="Percentage of Mito", xlab="Total Number of Genes Detected")
#hist(tenx_pbmc68k$total_counts/1e4, xlab="Library sizes (thousands)", main="",
#     breaks=20, col="grey80", ylab="Number of cells")
#hist(tenx_pbmc68k$total_features_by_counts, xlab="Number of expressed genes", main="",
#     breaks=20, col="grey80", ylab="Number of cells")
```
We remove cells with high proportion of mitocondrial 
reads, using it as a proxy for cell damage. 

```{r}
high_mito <- isOutlier(tenx_pbmc68k$pct_counts_Mito, 
                       nmads = 3, type="higher")
table(high_mito)

tenx_pbmc68k <- tenx_pbmc68k[,!high_mito]
tenx_pbmc68k
```

## Removing lowly expressed genes

Next, we remove the lowly expressed genes. Here, 
we keep only those genes that have at least 1 UMI 
in at least 5% of the data. These threshold are
dataset-specific and may need to be taylored to 
specific applications.

```{r}
num_reads <- 1
num_cells <- 0.01*ncol(tenx_pbmc68k)
system.time(keep <- which(DelayedArray::rowSums(counts(tenx_pbmc68k) >= num_reads ) >= num_cells))
tenx_pbmc68k <- tenx_pbmc68k[keep,]
tenx_pbmc68k
```

These leaves us with `length(keep)` genes.


Save tenx_pbmc68k object to /data/full
```{r}
library(HDF5Array)
saveHDF5SummarizedExperiment(tenx_pbmc68k, 
                             dir = here("main/case_studies/data/full/tenx_pbmc68k", "tenx_pbmc68k_preprocessed"), 
                             prefix="", replace=TRUE, 
                             chunkdim=c(dim(counts(tenx_pbmc68k))[1],1), 
                             level=NULL, verbose=FALSE)
```
