---
title: Testing blockapply vs beachmat
author: Davide Risso
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, 
                      error = FALSE, message = FALSE, 
                      cache = FALSE)
```


Here, I compare the current approach for label assignments to centroids to a simpler approach that uses the `blockApply` function.

# Time

## HDF5

```{r}
suppressPackageStartupMessages(library(HDF5Array))
suppressPackageStartupMessages(library(here))
suppressPackageStartupMessages(library(mbkmeans))
```

```{r}
data_name <- "TENxBrainData_75k"
sce <- loadHDF5SummarizedExperiment(dir = here("main/case_studies/data/full",
                                               data_name, 
                                               paste0(data_name, 
                                                      "_preprocessed")),
                                    prefix="")
sce
```

Compute centroids.

```{r}
system.time(mbk <- mbkmeans(counts(sce), clusters=15, batch_size = 100, num_init=1, 
                max_iters=100, compute_labels = FALSE))
```

Compute labels, the old way.

```{r}
system.time(labels <- predict_mini_batch(t(counts(sce)), mbk$centroids))
```

Compute labels, a simple apply.

```{r}
one_label <- function(x, centroids) {
  which.min(colSums((x - t(centroids))^2))
}

system.time(labels2 <- apply(as.matrix(counts(sce)), 2, one_label, centroids = mbk$centroids))
stopifnot(all(labels == labels2))
```

Compute labels, apply to centroids not to data.

```{r}
one_centroid <- function(x, data) {
  colSums((x - data)^2)
}

all_labels <- function(data, centroids) {
  ss <- apply(mbk$centroids, 1, one_centroid, data = data)
  apply(ss, 1, which.min)
}

system.time(labels3 <- all_labels(as.matrix(counts(sce)), mbk$centroids))
stopifnot(all(labels == labels3))
```

Compute labels, blockApply.

```{r}
system.time(labels4 <- blockApply(counts(sce), all_labels, centroids = mbk$centroids))
stopifnot(all(labels == unlist(labels4)))
```

## In-memory

Create in memory matrix.

```{r}
counts <- as.matrix(counts(sce))
```

Compute centroids.

```{r}
system.time(mbk <- mbkmeans(counts, clusters=15, batch_size = 100, num_init=1, 
                max_iters=100, compute_labels = FALSE))
```

Compute labels, the old way.

```{r}
system.time(labels <- predict_mini_batch(t(counts), mbk$centroids))
```

Compute labels, a simple apply.

```{r}
system.time(labels2 <- apply(counts, 2, one_label, centroids = mbk$centroids))
stopifnot(all(labels == labels2))
```

Compute labels, apply to centroids not to data.

```{r}
system.time(labels3 <- all_labels(as.matrix(counts), mbk$centroids))
stopifnot(all(labels == labels3))
```

Compute labels, blockApply.

```{r}
system.time(labels4 <- blockApply(counts, all_labels, centroids = mbk$centroids))
stopifnot(all(labels == unlist(labels4)))
```
