---
title: Graph-based clustering of 1.3M neurons data
author: Davide Risso
output: 
    html_document:
        theme: cosmo 
        toc: true
        toc_float: true
        highlight: tango
        number_sections: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, results = "markup")
```

```{r, message=FALSE}
library(here)
library(HDF5Array)
library(SingleCellExperiment)
library(scran)
library(igraph)
# library(leiden)
library(bluster)
nworkers <- 6
```


```{r load}
sce <- loadHDF5SummarizedExperiment(dir = here("main/case_studies/data/full/TENxBrainData/TENxBrainData_preprocessed"))
sce
```

# Clustering in PCA space

Here, we compare the mbkmeans clustering in PCA space to `scran`'s graph-based clustering.

To do so, we assume that all the preprocessing was done as in `full_analysis.Rmd` and we start from PCA.

## Approximate neighbors with Annoy

```{r graph_pca}
time.start <- proc.time()
g <- buildSNNGraph(sce, k=10, use.dimred = "PCA", 
                   BPPARAM = BiocParallel::MulticoreParam(nworkers),
                   BNPARAM = BiocNeighbors::AnnoyParam())
time.end <- proc.time()

time <- time.end - time.start
cat("Creating graph:", time[3]/60, "mins")
```

## Exact neighbors

```{r graph_pca_exact, eval=FALSE}
time.start <- proc.time()
g_exact <- buildSNNGraph(sce, k=10, use.dimred = "PCA", 
                   BPPARAM = BiocParallel::MulticoreParam(nworkers))
time.end <- proc.time()

time <- time.end - time.start
cat("Creating graph (exact):", time[3]/60, "mins")
```

## Louvain clustering

```{r louvain}
time.start <- proc.time()
clust <- cluster_louvain(g)$membership
time.end <- proc.time()

time <- time.end - time.start
cat("Louvain clustering:", time[3]/60, "mins")
```

## Leiden clustering

The Leiden algorithm (default values) fails with 64GB of RAM.

```{r leiden, eval=FALSE}
time.start <- proc.time()
clust_leiden <- leiden(g)
time.end <- proc.time()

time <- time.end - time.start
cat("Leiden clustering:", time[3]/60, "mins")
```

## Compare to mbkmeans

```{r compare}
# km_res <- readRDS(here("main/case_studies/data/full/TENxBrainData",
#                        "mbkmeans_pca50_k15-30_bs500.rds"))
# names(km_res) <- paste0("k", seq(15, 30))
cl1 <- sce$mbk_15
cl1_names <- names(sort(table(cl1)))
cl1 <- factor(cl1, levels=cl1_names)

cl2 <- clust
cl2_names <- names(sort(table(cl2)))
cl2 <- factor(cl2, levels=cl2_names)

heatmap(table(cl1, cl2), ylab="mbkmeans (k=15)", xlab="Louvain", Rowv = NA, Colv = NA)
# heatmap(table(km_res$k15$Clusters, clust_leiden), ylab="mbkmeans", xlab="Leiden")
# table(km_res$k15, clust_leiden)
mclust::adjustedRandIndex(sce$mbk_15, clust)
```

# Clustering of full matrix

The makeSNNGraph function fails with 64GB of RAM.

```{r graph_full, eval=FALSE}
time.start <- proc.time()
g_full <- makeSNNGraph(logcounts(sce), k=10,
                   BPPARAM = BiocParallel::MulticoreParam(nworkers),
                   BNPARAM = BiocNeighbors::AnnoyParam())
time.end <- proc.time()

time <- time.end - time.start
cat("Creating graph (full matrix):", time[3]/60, "mins")

time.start <- proc.time()
clust_full <- cluster_louvain(g_full)$membership
time.end <- proc.time()

time <- time.end - time.start
cat("Louvain clustering:", time[3]/60, "mins")
```

# Scanpy and bbknn

Here, we have run a complete pipeline in scanpy, using the bbknn method to remove batch effects (the mouse) and we compare the resulting clustering from Leiden with our mbkmeans results.

```{r scanpy_res}
library(dplyr)
scanpy_res <- read.csv(here("main/python/1M_neurons_leiden_labels.csv"))

df <- inner_join(as.data.frame(colData(sce)), scanpy_res, by = c("Barcode"="X"))
```

```{r compare_scanpy}
cl1 <- df$mbk_15
cl1_names <- names(sort(table(cl1)))
cl1 <- factor(cl1, levels=cl1_names)

cl2 <- df$leiden
cl2_names <- names(sort(table(cl2)))
cl2 <- factor(cl2, levels=cl2_names)

heatmap(table(cl1, cl2), ylab="mbkmeans (k=15)", xlab="Leiden", Rowv = NA, Colv = NA)

# heatmap(table(df$mbk_15, df$leiden), ylab="mbkmeans (k=15)", xlab="Leiden (scanpy)")
barplot(table(df$leiden))
heatmap(table(df$mbk_15, df$Mouse), ylab="mbkmeans (k=15)", xlab="Mouse", scale = "none")
heatmap(table(df$leiden, df$Mouse), xlab="Mouse", ylab="Leiden (scanpy)", scale="none")
mclust::adjustedRandIndex(df$mbk_15, df$leiden)
mclust::adjustedRandIndex(df$mbk_15, df$Mouse)
mclust::adjustedRandIndex(df$leiden, df$Mouse)
```

# Session Info

```{r sessioninfo}
library(benchmarkme)
print(sessionInfo())
print(get_ram())
print(get_cpu())
```
