---
title: 'Chunk-size Test: Time'
author: "Ruoxi Liu"
date: "3/17/2020"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,fig.width = 12, fig.height = 10)
```

```{r}
library(tidyr)
library(ggplot2)
library(gridExtra)
library(dplyr)
library(grid)
library(here)
```

```{r}
time_blockApp <- read.csv("/Users/April30/benchmark-hdf5-clustering/ongoing_analysis/ChunkTest/TENxBrainData/Output/new_time_blockapp.csv", header=TRUE, sep=",")
time_blockApp$label2 <- factor(time_blockApp$label2, levels = c("mbkmeans", "Best-HDF5", "Worst-HDF5"))
time_blockApp_steps <- time_blockApp %>% 
  filter(choice == "two steps")  %>% 
  gather(calc_label, time, time1:time3) %>%
  mutate(calc_label = replace(calc_label, calc_label == 'time1', "Load")) %>%
  mutate(calc_label = replace(calc_label, calc_label == 'time2', "Centroid")) %>%
  mutate(calc_label = replace(calc_label, calc_label == 'time3', "Labels")) 
time_blockApp_full <- time_blockApp %>% 
  filter(choice == "full")  %>% 
  gather(calc_label, time, time1:time3) %>%
  mutate(calc_label = replace(calc_label, calc_label == 'time1', "Whole")) %>%
  na.omit()
time_blockApp <- rbind(time_blockApp_steps,time_blockApp_full)
  

time_old <- read.csv("/Users/April30/benchmark-hdf5-clustering/ongoing_analysis/ChunkTest/TENxBrainData/Output/before_BloackApp/new_time_getrow.csv", header=TRUE, sep=",")
time_old$label2 <- factor(time_old$label2, levels = c("mbkmeans-OLD", "Best-HDF5-OLD", "Worst-HDF5-OLD"))
time_old_steps <- time_old %>% 
  filter(choice == "two steps")  %>% 
  gather(calc_label, time, time1:time3) %>%
  mutate(calc_label = replace(calc_label, calc_label == 'time1', "Load")) %>%
  mutate(calc_label = replace(calc_label, calc_label == 'time2', "Centroid")) %>%
  mutate(calc_label = replace(calc_label, calc_label == 'time3', "Labels")) 
time_old_full <- time_old %>% 
  filter(choice == "full")  %>% 
  gather(calc_label, time, time1:time3) %>%
  mutate(calc_label = replace(calc_label, calc_label == 'time1', "Whole")) %>%
  na.omit()
time_old <- rbind(time_old_steps,time_old_full)

time <- rbind(time_blockApp, time_old)
```

# Time
```{r}
p_time <- time_blockApp %>% 
  filter(calc_label !="Load") %>%
  dplyr::group_by(observations, abs.batch.size, label2) %>% 
  ggplot(aes(x = as.factor(abs.batch.size), y = time/60, color = label2)) +
          geom_point()+
    labs(title = "Time: Three Measures Side by Side (blockApply)") + 
    xlab("Absolute Batch Size")+
    ylab("Time(Minutes)")+
    facet_grid(~observations+calc_label)
#p_time
```
```{r}
p_time2 <- time_old %>% 
  filter(calc_label !="Load") %>%
  dplyr::group_by(observations, abs.batch.size, label2) %>% 
  ggplot(aes(x = as.factor(abs.batch.size), y = time/60, color = label2)) +
          geom_point()+
    labs(title = "Time: Three Measures Side by Side (with getrow)") + 
    xlab("Absolute Batch Size")+
    ylab("Time(Minutes)")+
    facet_grid(~observations+calc_label)
#p_time2
```


```{r}
require(gridExtra)
p_time_combine <- grid.arrange(p_time, p_time2, ncol=2)
```

### Take aways: Time analysis makes sense now
1. The relationship between mbkmeans and best HDF5 is what we saw before. it’s faster to use mbkmeans in memory. This makes sense.

2. Worst HDF5 is the slowest. This makes sense too.

3. the slowest part of the process is predicting the labels. this makes sense because we are loading in the obs into memory 1 at a time (for our old method with getrow).


```{r eval = FALSE, echo = FALSE}
# Compare blockApply with getrow
p_time_compare_mbkm1 <- time %>% 
  filter(calc_label=="Labels") %>%
  filter(label2=="mbkmeans"|label2=="mbkmeans-OLD") %>%
  dplyr::group_by(observations, abs.batch.size, label2) %>% 
  ggplot(aes(x = as.factor(abs.batch.size), y = time/60, color = label2)) +
          geom_point()+
    xlab("Absolute Batch Size")+
    ylab("Time(Minutes)")+
    labs(title = "Time Comparison: mbkmeans computing the labels") + 
    facet_grid(~observations)
p_time_compare_mbkm1
```

```{r eval = FALSE, echo = FALSE}
p_time_compare_mbkm2 <- time %>% 
  filter(calc_label=="Whole") %>%
  filter(label2=="mbkmeans"|label2=="mbkmeans-OLD") %>%
  dplyr::group_by(observations, abs.batch.size, label2) %>% 
  ggplot(aes(x = as.factor(abs.batch.size), y = time/60, color = label2)) +
          geom_point()+
    xlab("Absolute Batch Size")+
    ylab("Time(Minutes)")+
    labs(title = "Time Comparison: mbkmeans whole process") + 
    facet_grid(~observations)
p_time_compare_mbkm2
```

```{r eval = FALSE, echo = FALSE}
p_time_compare_hdf51 <- time %>% 
  filter(calc_label=="Labels") %>%
  filter(label2=="Best-HDF5"|label2=="Best-HDF5-OLD") %>%
  dplyr::group_by(observations, abs.batch.size, label2) %>% 
  ggplot(aes(x = as.factor(abs.batch.size), y = time/60, color = label2)) +
          geom_point()+
    xlab("Absolute Batch Size")+
    ylab("Time(Minutes)")+
    labs(title = "Time Comparison: hdf5-best computing the labels") + 
    facet_grid(~observations)
p_time_compare_hdf51
```
```{r eval = FALSE, echo = FALSE}
p_time_compare_hdf52 <- time %>% 
  filter(calc_label=="Whole") %>%
  filter(label2=="Best-HDF5"|label2=="Best-HDF5-OLD") %>%
  dplyr::group_by(observations, abs.batch.size, label2) %>% 
  ggplot(aes(x = as.factor(abs.batch.size), y = time/60, color = label2)) +
          geom_point()+
    xlab("Absolute Batch Size")+
    ylab("Time(Minutes)")+
    labs(title = "Time Comparison: hdf5-best whole process") + 
    facet_grid(~observations)
p_time_compare_hdf52
```
