---
title: 'Chunk-size Test: Time'
author: "Ruoxi Liu"
date: "3/17/2020"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,fig.width = 12, fig.height = 10)
```

```{r}
library(tidyr)
library(ggplot2)
library(gridExtra)
library(dplyr)
library(grid)
library(here)
```

```{r}
time_blockApp <- read.csv("/Users/April30/benchmark-hdf5-clustering/ongoing_analysis/ChunkTest/TENxBrainData/Output/new_time.csv", header=TRUE, sep=",")
time_blockApp$label2 <- factor(time_blockApp$label2, levels = c("mbkmeans", "Best-HDF5", "Worst-HDF5"))
time_blockApp_steps <- time_blockApp %>% 
  filter(choice == "two steps")  %>% 
  gather(calc_label, time, time1:time3) %>%
  mutate(calc_label = replace(calc_label, calc_label == 'time1', "Load")) %>%
  mutate(calc_label = replace(calc_label, calc_label == 'time2', "Centroid")) %>%
  mutate(calc_label = replace(calc_label, calc_label == 'time3', "Labels")) 
time_blockApp_full <- time_blockApp %>% 
  filter(choice == "full")  %>% 
  gather(calc_label, time, time1:time3) %>%
  mutate(calc_label = replace(calc_label, calc_label == 'time1', "Whole")) %>%
  na.omit()
time_blockApp <- rbind(time_blockApp_steps,time_blockApp_full)
  

time_old <- read.csv("/Users/April30/benchmark-hdf5-clustering/ongoing_analysis/ChunkTest/TENxBrainData/Output/before_BloackApp/new_time_old.csv", header=TRUE, sep=",")
time_old$label2 <- factor(time_old$label2, levels = c("mbkmeans-OLD", "Best-HDF5-OLD", "Worst-HDF5-OLD"))
time_old_steps <- time_old %>% 
  filter(choice == "two steps")  %>% 
  gather(calc_label, time, time1:time3) %>%
  mutate(calc_label = replace(calc_label, calc_label == 'time1', "Load")) %>%
  mutate(calc_label = replace(calc_label, calc_label == 'time2', "Centroid")) %>%
  mutate(calc_label = replace(calc_label, calc_label == 'time3', "Labels")) 
time_old_full <- time_old %>% 
  filter(choice == "full")  %>% 
  gather(calc_label, time, time1:time3) %>%
  mutate(calc_label = replace(calc_label, calc_label == 'time1', "Whole")) %>%
  na.omit()
time_old <- rbind(time_old_steps,time_old_full)

time <- rbind(time_blockApp, time_old)
```

# Time
```{r}
p_time <- time_blockApp %>% 
  filter(calc_label !="Load") %>%
  dplyr::group_by(observations, abs.batch.size, label2) %>% 
  ggplot(aes(x = as.factor(abs.batch.size), y = time/60, color = label2)) +
          geom_point()+
    labs(title = "Time: Three Measures Side by Side (blockApply())") + 
    xlab("Absolute Batch Size")+
    ylab("Time(Minutes)")+
    facet_grid(~observations+calc_label)
p_time
```
```{r}
p_time2 <- time_old %>% 
  filter(calc_label !="Load") %>%
  dplyr::group_by(observations, abs.batch.size, label2) %>% 
  ggplot(aes(x = as.factor(abs.batch.size), y = time/60, color = label2)) +
          geom_point()+
    labs(title = "Time: Three Measures Side by Side (with getrow())") + 
    xlab("Absolute Batch Size")+
    ylab("Time(Minutes)")+
    facet_grid(~observations+calc_label)
p_time2
```

### Take aways:
1. The relationship between mbkmeans and best HDF5 is what we saw before. it’s faster to use mbkmeans in memory. This makes sense.

2. Worst HDF5 is the slowest (when you assess the whole process).  This makes sense too.

3. the slowest part of the process is predicting the labels. this makes sense because we are loading in the obs into memory 1 at a time.

4. for computing centroids, worst HDF5 is the slowest. This makes sense.

5. for computing labels, best HDF5 is the slowest. This does not make sense.

# Compare blockApply with getrow
```{r}
p_time_compare_mbkm1 <- time %>% 
  filter(calc_label=="Labels") %>%
  filter(label2=="mbkmeans"|label2=="mbkmeans-OLD") %>%
  dplyr::group_by(observations, abs.batch.size, label2) %>% 
  ggplot(aes(x = as.factor(abs.batch.size), y = time/60, color = label2)) +
          geom_point()+
    xlab("Absolute Batch Size")+
    ylab("Time(Minutes)")+
    labs(title = "Time Comparison: mbkmeans computing the labels") + 
    facet_grid(~observations)
p_time_compare_mbkm1
```

```{r}
p_time_compare_mbkm2 <- time %>% 
  filter(calc_label=="Whole") %>%
  filter(label2=="mbkmeans"|label2=="mbkmeans-OLD") %>%
  dplyr::group_by(observations, abs.batch.size, label2) %>% 
  ggplot(aes(x = as.factor(abs.batch.size), y = time/60, color = label2)) +
          geom_point()+
    xlab("Absolute Batch Size")+
    ylab("Time(Minutes)")+
    labs(title = "Time Comparison: mbkmeans whole process") + 
    facet_grid(~observations)
p_time_compare_mbkm2
```

```{r}
p_time_compare_hdf51 <- time %>% 
  filter(calc_label=="Labels") %>%
  filter(label2=="Best-HDF5"|label2=="Best-HDF5-OLD") %>%
  dplyr::group_by(observations, abs.batch.size, label2) %>% 
  ggplot(aes(x = as.factor(abs.batch.size), y = time/60, color = label2)) +
          geom_point()+
    xlab("Absolute Batch Size")+
    ylab("Time(Minutes)")+
    labs(title = "Time Comparison: hdf5-best computing the labels") + 
    facet_grid(~observations)
p_time_compare_hdf51
```
```{r}
p_time_compare_hdf52 <- time %>% 
  filter(calc_label=="Whole") %>%
  filter(label2=="Best-HDF5"|label2=="Best-HDF5-OLD") %>%
  dplyr::group_by(observations, abs.batch.size, label2) %>% 
  ggplot(aes(x = as.factor(abs.batch.size), y = time/60, color = label2)) +
          geom_point()+
    xlab("Absolute Batch Size")+
    ylab("Time(Minutes)")+
    labs(title = "Time Comparison: hdf5-best whole process") + 
    facet_grid(~observations)
p_time_compare_hdf52
```
