---
title: "Memory_time_series"
author: "Ruoxi Liu"
date: "3/20/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
```

Uses TENxBrain Data 500k subset.

## HDF5

The codes for benchmarking are as the following:

"""

Rprof(filename = here("main/case_studies/output/Memory_output",paste0(method, out_name)), append = FALSE, memory.profiling = TRUE)

sce <- loadHDF5SummarizedExperiment(dir = here("main/case_studies/data/subset/TENxBrainData", data_name, paste0(data_name, "_preprocessed_best")), prefix="")
    
invisible(mbkmeans(counts(sce), clusters=k, batch_size = as.integer(dim(counts(sce))[2]*batch), num_init=1, max_iters=100))

Rprof(NULL)

"""

### 2% batch size (10,000 cells per batch)
```{r}
profile_hdf5_500k_0.02bs <- summaryRprof(filename = "/Users/April30/benchmark-hdf5-clustering/main/case_studies/output/Memory_output/hdf5TENxBrainData_500k_ruoxi_cluster_step1_Mar15235849.852_0.02.out", chunksize = -1L, memory = "tseries", diff = FALSE)
df_hdf5_500k_0.02bs <- rowSums(profile_hdf5_500k_0.02bs[,1:3])*0.00000095367432
df_hdf5_500k_0.02bs <- as.data.frame(df_hdf5_500k_0.02bs)

#line #1-259: loadHDF5SummarizedExperiment
#line #262-19213 : "mini_batch" ".local" "mbkmeans" "mbkmeans" 
#line #19214-46105: predict_mini_batch_r

df_hdf5_500k_0.02bs_2 <- tibble::rownames_to_column(df_hdf5_500k_0.02bs, "Time")
df_hdf5_500k_0.02bs_2[which.max(df_hdf5_500k_0.02bs_2$df_hdf5_500k_0.02bs), ] 
#the peak of memory happens at the 130.58th second, with the usage of 16.86 GB (at line #6529).
profile_hdf5_500k_0.02bs["130.58",]

plot(rownames(df_hdf5_500k_0.02bs),df_hdf5_500k_0.02bs$df_hdf5_500k_0.02bs/1024,type="l", xlab="Time(seconds)", ylab="Memory(GB)", main = "Memory Usage on 500k data with 10,000 batch size: HDF5")
abline(v=261*0.02, col="blue")
abline(v=19213*0.02, col="red")
abline(v=33,col="brown")
text(1, 15, "load \ndata", cex = .7, col = "blue")
text(200, 15, "mbkmeans::mini_batch", cex = .7, col = "red")
text(600, 15, "mbkmeans::predict_mini_batch_r", cex = .7, col = "red")
```

### 0.2% batch size (1,000 cells per batch)
```{r}
profile_hdf5_500k_0.002bs <- summaryRprof(filename = "/Users/April30/benchmark-hdf5-clustering/main/case_studies/output/Memory_output/hdf5TENxBrainData_500k_ruoxi_cluster_step1_Mar15224414.914_0.002.out", chunksize = -1L, memory = "tseries", diff = FALSE)
df_hdf5_500k_0.002bs <- rowSums(profile_hdf5_500k_0.002bs[,1:3])*0.00000095367432
df_hdf5_500k_0.002bs <- as.data.frame(df_hdf5_500k_0.002bs)

#line #1-357: loadHDF5SummarizedExperiment
#line #361-16098 : "mini_batch" ".local" "mbkmeans" "mbkmeans" 
#line #16099-49332: predict_mini_batch_r

df_hdf5_500k_0.002bs_2 <- tibble::rownames_to_column(df_hdf5_500k_0.002bs, "Time")
df_hdf5_500k_0.002bs_2[which.max(df_hdf5_500k_0.002bs_2$df_hdf5_500k_0.002bs), ] 
#the peak of memory happens at the 159.48th second, with the usage of 16.86 GB (at line #7974).
profile_hdf5_500k_0.02bs["159.48",]

plot(rownames(df_hdf5_500k_0.002bs),df_hdf5_500k_0.002bs$df_hdf5_500k_0.002bs/1024,type="l", xlab="Time(seconds)", ylab="Memory(GB)", main = "Memory Usage on 500k data with 1,000 batch size: HDF5")
abline(v=360*0.02, col="blue")
abline(v=16098*0.02, col="red")
text(1, 15, "load \ndata", cex = .7, col = "blue")
text(200, 15, "mbkmeans::mini_batch", cex = .7, col = "red")
text(600, 15, "mbkmeans::predict_mini_batch_r", cex = .7, col = "red")
```

## mbkmeans

The codes for benchmarking are as the following:

"""

Rprof(filename = here("main/case_studies/output/Memory_output",paste0(method, out_name)), append = FALSE, memory.profiling = TRUE)

sce <- loadHDF5SummarizedExperiment(dir = here("main/case_studies/data/subset/TENxBrainData", data_name, paste0(data_name, "_preprocessed_best")), prefix="")

sce_km <- realize(counts(sce))

invisible(mbkmeans(sce_km, clusters=k, batch_size = as.integer(dim(counts(sce))[2]*batch), num_init=1, max_iters=100))

Rprof(NULL)

"""

### 2% batch size (10,000 cells per batch)
```{r}
profile_mbkm_500k_0.02bs <- summaryRprof(filename = "/Users/April30/benchmark-hdf5-clustering/main/case_studies/output/Memory_output/mbkmeansTENxBrainData_500k_ruoxi_cluster_step1_Mar15235544.857_0.02.out", chunksize = -1L, memory = "tseries", diff = FALSE)
df_mbkm_500k_0.02bs <- rowSums(profile_mbkm_500k_0.02bs[,1:3])*0.00000095367432
df_mbkm_500k_0.02bs <- as.data.frame(df_mbkm_500k_0.02bs)

#line #1-249: loadHDF5SummarizedExperiment
#line #250-2719: realize
#line #2720-19037 : "mini_batch" ".local" "mbkmeans" "mbkmeans" 
#line #19038-43815: predict_mini_batch_r

df_mbkm_500k_0.02bs_2 <- tibble::rownames_to_column(df_mbkm_500k_0.02bs, "Time")
df_mbkm_500k_0.02bs_2[which.max(df_mbkm_500k_0.02bs_2$df_mbkm_500k_0.02bs), ] 
#the peak of memory happens at the 315.62th second, with the usage of 27.70 GB (at line #15781).
profile_hdf5_500k_0.02bs["315.62",]

plot(rownames(df_mbkm_500k_0.02bs),df_mbkm_500k_0.02bs$df_mbkm_500k_0.02bs/1024,type="l", xlab="Time(seconds)", ylab="Memory(GB)", main = "Memory Usage on 500k data with 10,000 batch size: mbkmeans")
abline(v=248*0.02, col="blue")
abline(v=2718*0.02, col="green")
abline(v=19036*0.02, col="red")
text(0.1, 25, "load \ndata", cex = .7, col = "blue")
text(40, 25, "realize", cex = .7, col = "green")
text(200, 10, "mbkmeans::mini_batch", cex = .7, col = "red")
text(600, 10, "mbkmeans::predict_mini_batch_r", cex = .7, col = "red")
```
```{r}
#memory_compare1 <- profvis(prof_input = "/Users/April30/benchmark-hdf5-clustering/main/case_studies/output/Memory_output/hdf5TENxBrainData_500k_ruoxi_cluster_step1_Mar15235849.852_0.02.out")
#htmlwidgets::saveWidget(memory_compare1, "/Users/April30/profvis_kmeans.html")
```

```{r eval=FALSE}
profile_hdf5_500k_10G <- summaryRprof(filename = "/Users/April30/benchmark-hdf5-clustering/main/case_studies/output/Memory_output/hdf5TENxBrainData_500k_ruoxi_cluster_step1_Mar24134656.445_0.02.out", chunksize = -1L, memory = "tseries", diff = FALSE)
df_hdf5_500k_10G <- rowSums(profile_hdf5_500k_10G[,1:3])*0.00000095367432
df_hdf5_500k_10G <- as.data.frame(df_hdf5_500k_10G)

#line #1-277: loadHDF5SummarizedExperiment
#line #278-1866 : "mini_batch" ".local" "mbkmeans" "mbkmeans" 


df_hdf5_500k_10G_2 <- tibble::rownames_to_column(df_hdf5_500k_10G, "Time")
df_hdf5_500k_10G_2[which.max(df_hdf5_500k_10G_2$df_hdf5_500k_10G), ] 
#the peak of memory happens at the 35.8th second, with the usage of 7.5 GB (at line #1790).


plot(rownames(df_hdf5_500k_10G),df_hdf5_500k_10G$df_hdf5_500k_10G/1024,type="l", xlab="Time(seconds)", ylab="Memory(GB)", main = "Memory Usage on 500k data with 10,000 batch size: 10G")
abline(v=276*0.02, col="blue")
abline(v=19213*0.02, col="red")
text(1, 6, "load \ndata", cex = .7, col = "blue")
text(20, 6, "mbkmeans::mini_batch", cex = .7, col = "red")
#text(600, 15, "mbkmeans::predict_mini_batch_r", cex = .7, col = "red")
```